Fields COVID-19 dataset exploration

### 2023-01-04 data_cleaning/Data_cleaning_and_covariates_Jan_03.qmd
Updated
need to check proportions for weights

>>>>

# Raking

The next step is to adjust the variables according to the Census data (raking). I will follow the steps provided by [https://sdaza.com/blog/2012/raking/](https://sdaza.com/blog/2012/raking/) https://www.r-bloggers.com/2018/12/survey-raking-an-illustration/

The variables to define raking weights are:

  - income
  - age groups 
  - geographical location
  - race and ethnicity: check proportions here https://www.ontario.ca/document/2016-census-highlights/fact-sheet-9-ethnic-origin-and-visible-minorities

```{r,define-target-list}

library(weights)

#get percentages
wpct(clean_data$income)
wpct(clean_data$age_group)
wpct(clean_data$race)

#create target list for weights

age_group<-c(0.127,0.129,0.128,0.149,0.137,0.167)

race<-c(0.016,0.047,0.066,)

income<-c(0.075,0.116,0.154,0.195,)
